More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Cleaned up sorts

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
\item[$\bullet$] $Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
hole $j$.

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$.

@@

\begin{definition}[Sorts, Holes, Leaves of pNets]
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform. In the definition of sorts, we do not need to distinguish
input variables (that specify the dataflow within LTSs), so for
computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
operation.} to remove the
\emph{input marker} of variables. Formally:
\[
\begin{array}{l}
\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sort(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!,
\overline{\symb{SV}}\myrangle)
=\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
\end{array}
\]

\item
The set of holes of a pNet is defined inductively; the sets of holes
in a pNet node and its subnets are all disjoint:
  \[\begin{array}{l}
\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
\Holes(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
\[\begin{array}{l}
\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
\Leaves(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
\end{array}\]
\end{itemize}
\end{definition}

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \xrightarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{Sort},\symb{SV}_k^{k\in K} \myrangle$
be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
\end{array}\]

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

\begin{definition}[pNet composition]
	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$
 can be (partially) filled by providing  a pNets $\pNet'$ of the
	right sort to fill one of  its holes.	
	Suppose $j_0\in J$:
	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
	%%J\setminus L},
	%% \symb{SV}_k^{k\in K}\myrangle
	%% \]
	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},Sort_j^{j\in J\setminus \{j_0\}},
	\overline{\symb{SV}}\myrangle
	\]
\end{definition}

\LUDO{added congruence theorem below}
\begin{theorem}[Congruence]\label{thm-congr-eq}
	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
	$\Sort(Q)=\Sort(Q')=Sort_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
	strong bisimilarity.}. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet[Q']_{j_0}$ are FH-bisimilar.
\end{theorem}

\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
	Consider two FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	Sort_j^{j\in 
	J}, 	\overline{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=Sort_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
\end{theorem}

@@

	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
	Sort_{P21} \land t2 = tgt2_2
	\land v \!= \! \underline{um(t2)} )  $
	In the broadcast examples, we do not use assignments and will omit the \Post part of 
	the open transition.
\end{example}

@@

$Pred_{UM\_21} =  [um(t1)=b \land b\in Sort_{P21} \land um(t1)=v_{SG2}]$

@@

%% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
%%   b\in Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
%%   \land v = \tau]  $

@@

That can be simplified (eliminating the vector local variables and the
intermediate resulting actions), as: $Pred1 = [b\in Sort_{P21}
  \land b=um(tgt2_2) \land v=\underline{b} ]  $

@@

\begin{mathpar}
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred_{Root}}
         {\ostate{020} \xrightarrow{v} \ostate{100}}
\end{mathpar}
with
$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
  b\in Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $

@@

$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in Sort_{P3}  \land v = \underline{bm(t3)}]$

@@

$Pred2 = [tgt1_1=tgt2_2 \land
  b\in Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
$

@@

\begin{eqnarray*}
OT_1 & = \openrule
         {0 \xrightarrow{ium(?tgt2)}_{gw2} 2 \quad
           \xrightarrow{b1}_{P21}
          \quad P1}
         {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
 with & P1 = [b1\in Sort_{P21} \land b1=um(tgt2_2) ]
 \\
OT_2 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b2}_{P3}
           \quad P2}
         {\ostate{020} \xrightarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
         with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
           \land  b2\in Sort_{P3} \land b2=um(tgt2_2) ]
         \\
OT_3 & = \openrule
         {1 \xrightarrow{dm(tgt1_1)}_{gw1} 0 \quad
           0 \xrightarrow{im(?tgt11_1)}_{gw11} 1 \quad
           \xrightarrow{b3}_{P12}
           \quad P3}
         {\ostate{100} \xrightarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
         with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
           \land  b3\in Sort_{P12} \land b3=im(tgt1_1) ]
         \\
OT_4 & = \openrule
         { 1 \xrightarrow{dm(tgt11_1)}_{gw11} 0 \quad
           \xrightarrow{b4}_{P111}
           \quad P4}
         {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
 with & P4 = [ b4=im(tgt11_1) \land  b4\in Sort_{P111} \land IsAncestor(11,tgt11_1) ]
         \\
OT_5 & = \openrule
         {1 \xrightarrow{Discard}_{gw1} 0 \quad
           \quad P5}
         {\ostate{100} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P5 = [IsDirectRelative(1,tgt1_1) ]
 \\
OT_6 & = \openrule
         { 2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P6}
         {\ostate{020} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P6 = [ IsAncestor(2,tgt2_2) ]
 \\
OT_7 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
          0 \xrightarrow{im(?tgt2_1)}_{gw2} 1 \quad
          \xrightarrow{b7}_{P3}\quad
           \quad P7}
         {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
 with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in Sort_{P3} \land b7 = im(?a)  ]
 \\
OT_8 & = \openrule
         {2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P8}
         {\ostate{110} \xrightarrow{Discard} \ostate{100}}\\
 with & P8 = [ IsDirectRelative(2,tgt2_1) ]
\end{eqnarray*}

>>>>

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{DotArrow}

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
\emph{sort} of
hole $j$.

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$.

@@

\begin{definition}[Sorts, Holes, Leaves of pNets]
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform. In the definition of sorts, we do not need to distinguish
input variables (that specify the dataflow within LTSs), so for
computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
operation.} to remove the
\emph{input marker} of variables. Formally:
\[
\begin{array}{l}
\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
    J}\rangle} s'\in \to \} \\
\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
\overline{\pNet}\!,
\overline{\symb{SV}}\myrangle)
=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
\to\alpha'\in\set{\symb{SV}}\}
\end{array}
\]

\item
The set of holes of a pNet is defined inductively; the sets of holes
in a pNet node and its subnets are all disjoint:
  \[\begin{array}{l}
\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
=J\cup{\displaystyle \bigcup_{i\in 
I}\Holes(\pNet_i)}\\
\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
\[\begin{array}{l}
\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in 
I}\Leaves(\pNet_i)}
\end{array}\]
\end{itemize}
\end{definition}

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \xrightarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\symb{SV}_k^{k\in K} \myrangle$
be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
\end{array}\]

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $

@@

\begin{definition}[pNet composition]
	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$
 can be (partially) filled by providing  a pNets $\pNet'$ of the
	right sort to fill one of  its holes.	
	Suppose $j_0\in J$:
	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
	%%J\setminus L},
	%% \symb{SV}_k^{k\in K}\myrangle
	%% \]
	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
	\overline{\symb{SV}}\myrangle
	\]
\end{definition}

\LUDO{added congruence theorem below}
\begin{theorem}[Congruence]\label{thm-congr-eq}
	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
	ensured by 
	strong bisimilarity.}. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet[Q']_{j_0}$ are FH-bisimilar.
\end{theorem}

\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
	Consider two FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\overline{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
\end{theorem}

@@

	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
	\Sort_{P21} \land t2 = tgt2_2
	\land v \!= \! \underline{um(t2)} )  $
	In the broadcast examples, we do not use assignments and will omit the \Post part of 
	the open transition.
\end{example}

@@

$Pred_{UM\_21} =  [um(t1)=b \land b\in \Sort_{P21} \land um(t1)=v_{SG2}]$

@@

%% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
%%   b\in \Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
%%   \land v = \tau]  $

@@

That can be simplified (eliminating the vector local variables and the
intermediate resulting actions), as: $Pred1 = [b\in \Sort_{P21}
  \land b=um(tgt2_2) \land v=\underline{b} ]  $

@@

\begin{mathpar}
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred_{Root}}
         {\ostate{020} \xrightarrow{v} \ostate{100}}
\end{mathpar}
with
$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
  b\in \Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $

@@

$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in 
\Sort_{P3}  \land v = \underline{bm(t3)}]$

@@

$Pred2 = [tgt1_1=tgt2_2 \land
  b\in \Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
$

@@

\begin{eqnarray*}
OT_1 & = \openrule
         {0 \xrightarrow{ium(?tgt2)}_{gw2} 2 \quad
           \xrightarrow{b1}_{P21}
          \quad P1}
         {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
 with & P1 = [b1\in \Sort_{P21} \land b1=um(tgt2_2) ]
 \\
OT_2 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b2}_{P3}
           \quad P2}
         {\ostate{020} \xrightarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
         with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
           \land  b2\in \Sort_{P3} \land b2=um(tgt2_2) ]
         \\
OT_3 & = \openrule
         {1 \xrightarrow{dm(tgt1_1)}_{gw1} 0 \quad
           0 \xrightarrow{im(?tgt11_1)}_{gw11} 1 \quad
           \xrightarrow{b3}_{P12}
           \quad P3}
         {\ostate{100} \xrightarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
         with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
           \land  b3\in \Sort_{P12} \land b3=im(tgt1_1) ]
         \\
OT_4 & = \openrule
         { 1 \xrightarrow{dm(tgt11_1)}_{gw11} 0 \quad
           \xrightarrow{b4}_{P111}
           \quad P4}
         {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
 with & P4 = [ b4=im(tgt11_1) \land  b4\in \Sort_{P111} \land IsAncestor(11,tgt11_1) ]
         \\
OT_5 & = \openrule
         {1 \xrightarrow{Discard}_{gw1} 0 \quad
           \quad P5}
         {\ostate{100} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P5 = [IsDirectRelative(1,tgt1_1) ]
 \\
OT_6 & = \openrule
         { 2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P6}
         {\ostate{020} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P6 = [ IsAncestor(2,tgt2_2) ]
 \\
OT_7 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
          0 \xrightarrow{im(?tgt2_1)}_{gw2} 1 \quad
          \xrightarrow{b7}_{P3}\quad
           \quad P7}
         {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
 with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in \Sort_{P3} \land b7 = im(?a)  ]
 \\
OT_8 & = \openrule
         {2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P8}
         {\ostate{110} \xrightarrow{Discard} \ostate{100}}\\
 with & P8 = [ IsDirectRelative(2,tgt2_1) ]
\end{eqnarray*}
